Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd

### Recency {#sec-recency}
```{r}
#| label: fig-recency
#| fig-cap: Distribution of the recency of the polls after July 21 2024
#| echo: false
#| warning: false
#| message: false
ggplot(harris_data, aes(x = recency)) +
  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
  labs(
    x = "Recency (days)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
#| label: fig-percentage
#| fig-cap: Distribution of support percentage of Kamala Harris
#| echo: false
#| warning: false
#| message: false
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
  labs(
    x = "Support Percentage (%)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
#| label: tbl-category
#| tbl-cap: Summary Statistics of categorical variable population and national_pull
#| echo: false
#| warning: false
#| message: false
harris_data|>select(population,national_poll)|>
  datasummary_skim(type = "categorical")
```

### National Poll {#sec-national-poll}

@@

```{r}
#| label: fig-state
#| fig-cap: Count of polls by the US state 
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-numericgrade
#| fig-cap: Distribution of numeric grade
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-numericgradetime
#| fig-cap: Harris Support Over Time by Numeric Grade
#| echo: false
#| warning: false
#| message: false

>>>>

### Recency {#sec-recency}
```{r}
#| label: fig-recency
#| fig-cap: Distribution of the Poll Recency since July 21, 2024
#| echo: false
#| warning: false
#| message: false
ggplot(harris_data, aes(x = recency)) +
  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
  labs(
    x = "Recency (days)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
#| label: fig-percentage
#| fig-cap: Distribution of the Support Percentage of Kamala Harris
#| echo: false
#| warning: false
#| message: false
ggplot(harris_data, aes(x = pct)) +
  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
  labs(
    x = "Support Percentage (%)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
#| label: tbl-category
#| tbl-cap: Summary Statistics of the categorical variables population and national_pull
#| echo: false
#| warning: false
#| message: false
harris_data|>select(population,national_poll)|>
  datasummary_skim(type = "categorical")
```
### National Poll {#sec-national-poll}

@@

```{r}
#| label: fig-state
#| fig-cap: Count of Polls by the US state 
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-numericgrade
#| fig-cap: Distribution of the Numeric Grade of the Polls
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-numericgradetime
#| fig-cap: Harris Support Over Time by Numeric Grade of the polls
#| echo: false
#| warning: false
#| message: false
